On the Galaxy Size--Halo Connection

### 2017-08-30 paper/galsize_paper.tex
Updated draft with brief description of galaxy sample

@@

\subsubsection{Mapping $\mstar$ and $\sfr$ to halos}
\label{subsubsec:umachine}
The starting point of our model is the best-fit {\tt UniverseMachine} model \citep[][in prep]{behroozi_etal17}. This model maps stellar mass and star-formation rate to every halo and subhalo at each snapshot in the Bolshoi-Planck simulation. The stellar mass function, quenched fraction, SFR density, and SFR-dependent clustering are all accurately captured by this model from $z=0-10.$ The model we have developed in the present work does not depend in an essential way upon the {\tt UniverseMachine} model in particular, we only require some reasonably accurate starting point for the $\mstar$ and $\ssfr$ values mapped to simulated halos.

>>>>

Our galaxy sample comes from Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS][]{ahn_etal14}. We study the same $\mstar-$complete galaxy sample used in \citet{behroozi_etal15}, to which we refer the reader for details. Values for $\mstar$ and $\sfr$ are taken from the MPA-JHU value-added catalog \citep{kauffmann_etal03,brinchmann_etal04}.

@@

\subsubsection{Mapping $\mstar$ and $\sfr$ to halos}
\label{subsubsec:umachine}

The starting point of our model is the best-fit {\tt UniverseMachine} model \citep[][in prep]{behroozi_etal17}. This model maps stellar mass and star-formation rate to every halo and subhalo at each snapshot in the Bolshoi-Planck simulation. The stellar mass function, quenched fraction, SFR density, and SFR-dependent clustering are all accurately captured by this model from $z=0-10.$ The model we have developed in the present work does not depend in an essential way upon the {\tt UniverseMachine} model in particular, we only require some reasonably accurate starting point for the $\mstar$ and $\ssfr$ values mapped to simulated halos.
